---
title: "readme"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidyverse)
library(data.table)
library(broom)
library(tidyr)
```

## R Functional Programming 
This repository is to practice R Functional Programming. It will consist of series of practices. In practice 1, the use of package [tidyr] and [broom] will be explored, to pass functions, to tidy dataset using data frame. Practice 2 I will practice the use of [package data.table] along with [package broom]. [data.table] is underrepresented package that not only gives wide variety of applications in data wrangling, but also gives users fast data processing speed.  

Practice 1 starts with ...
```{r}
mtcars %>% group_by(cyl)%>%nest()
```

And the final product is...

```{r}
groupby_mtcars<-mtcars %>% group_by(cyl)%>%nest()

trait_model<-function(df,x.var,y.var){
  df %$%loess(.[[y.var]]~.[[x.var]])  
}

groupby_mtcars %>% 
  mutate(
    
    model=data%>%map(trait_model,"wt","mpg")
    
    
    
  )
```

Practice 2 starts with ...
```{r}
mtcars %>%data.table %>%head
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
