---
title: "readme"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidyverse)
library(data.table)
library(broom)
library(tidyr)
```

## R Functional Programming, inspired by [plotcon talk](https://rstudio-pubs-static.s3.amazonaws.com/237010_6d37553296a34a6c899f2660911f1b17.html) 
This repository is to practice R Functional Programming. It will consist of series of practices. In practice 1, the use of package [purrr](https://github.com/tidyverse/purrr), [tidyr](http://tidyr.tidyverse.org/) and [broom](https://cran.r-project.org/web/packages/broom/vignettes/broom.html) will be explored, to pass functions into data frame objects. Practice 2 I will practice the use of package [data.table](https://cran.r-project.org/web/packages/data.table/vignettes/datatable-intro.html) along with package broom. data.table is underrepresented package that not only gives wide variety of applications in data wrangling, but also gives users fast data processing speed.  

Practice 1 starts with ...
```{r}
mtcars %>% group_by(cyl)%>%nest()
```

definde function trait_model

```{r}
groupby_mtcars<-mtcars %>% group_by(cyl)%>%nest()

trait_model<-function(df,x.var,y.var){
  df %$%lm(.[[y.var]]~.[[x.var]])  
}

```


And use purrr::map to 
- pass function trait_model to the dataframe colum 'data' create new column 'model', 
- then to pass function broom::glance to the column 'model' for creating another new column 'summary'.
```{r}
groupby_mtcars %<>% 
  mutate(
    
    model=data%>%map(trait_model,"wt","mpg"),
    summary=model%>%map(broom::glance)
    
    
  )

```
Now groupby_mtcars looks like this:
```{r}
groupby_mtcars %>% head

```



Practice 2 starts with ...
```{r}
mtcars %>%data.table %>%head
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
